Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/design.tex
x
make spell

\paragraph{Optional.}
Nail includes an \cc{optional} combinator, which attempts to recognize a value, but succeeds
without consuming input when it cannot recognize that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.
For example, the grammar for  Ethernet headers uses \cc{optional vlan\_header} to parse the VLAN
header that only appears in Ethernet packets transmitted to a non-default VLAN.

\paragraph{References.}
Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.
The reference combinator does not need to used when another combinator, such as \cc{optional} or
\cc{many} already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.

\begin{figure}
\begin{verbatim}
expr = choose {
  PAREN = <uint8='('; *expr; uint8=')'>
  PRODUCT = sepBy1 uint8='*' expr
  SUM = sepBy1 uint8='+' expr
  INTEGER = many1 uint8 | '0' .. '9'
}
\end{verbatim} \cc{paren = < uint8="("; optional *paren; uint8=")" >}.
\label{fig:grammar-arith}
\caption{Grammar for sums and products of integers.}
\end{figure}
% To support recursive structures, we include a reference combinator \cc{*}, which
%   is syntactically equivalent to directly including the parser, but in the internal model adds a
%   level of indirection to the value. This allows recursive structures to be parsed, f

>>>>

\paragraph{Optional.}
Nail includes an \cc{optional} combinator, which attempts to recognize a value, but succeeds
without consuming input when it cannot recognize that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.
For example, the grammar for  Ethernet headers uses \cc{optional vlan\_header} to parse the VLAN
header that only appears in Ethernet packets transmitted to a non-default VLAN\@.

\paragraph{References.}
Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.
The reference combinator does not need to used when another combinator, such as \cc{optional} or
\cc{many}, already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.

\begin{figure}
\begin{verbatim}
expr = choose {
  PAREN = <uint8='('; *expr; uint8=')'>
  PRODUCT = sepBy1 uint8='*' expr
  SUM = sepBy1 uint8='+' expr
  INTEGER = many1 uint8 | '0' .. '9'
}
\end{verbatim} \cc{paren = < uint8="("; optional *paren; uint8=")" >}.
\caption{Grammar for sums and products of integers.}
\label{fig:grammar-arith}
\end{figure}
% To support recursive structures, we include a reference combinator \cc{*}, which
%   is syntactically equivalent to directly including the parser, but in the internal model adds a
%   level of indirection to the value. This allows recursive structures to be parsed, f

### 2014-05-02 paper/osdi14/eval.tex
make spell

Nail also protects against parsing ambiguity vulnerabilities like the four others we studied. First,
Nail grammars explicitly encode duplicated information such as the redundant length fields in ZIP
that caused a vulnerability in the Python ZIP library. Second, the other three vulnerabilities exist
because multiple implementations of the same protocol disagree on some inputs. Hand-written protocol
parsers are not very reuseable, as they build application specific data structures and are tightly
coupled to the rest of the code. Nail grammars, however, can be re-used between applications,
avoiding protocol misunderstandings.

>>>>

Nail also protects against parsing ambiguity vulnerabilities like the four others we studied. First,
Nail grammars explicitly encode duplicated information such as the redundant length fields in ZIP
that caused a vulnerability in the Python ZIP library. Second, the other three vulnerabilities exist
because multiple implementations of the same protocol disagree on some inputs. Hand-written protocol
parsers are not very reusable, as they build application specific data structures and are tightly
coupled to the rest of the code. Nail grammars, however, can be re-used between applications,
avoiding protocol misunderstandings.

### 2014-05-02 paper/osdi14/motivation.tex
make spell

We found 83 vulnerabilities in the CVE database~\cite{cve-database} that
that mention the search string ``ZIP.''  Just 16 of these vulnerabilities
were related to processing ZIP archives; the rest were unrelated to ZIP
archives or involved applications insecurely using the contents of untrusted
ZIP files.  Figure~\ref{fig:motivation} summarizes the 16 ZIP-related
vulnerabilities.

>>>>

We found 83 vulnerabilities in the CVE database~\cite{cve-database}
that mention the search string ``ZIP.''  Just 16 of these vulnerabilities
were related to processing ZIP archives; the rest were unrelated to ZIP
archives or involved applications insecurely using the contents of untrusted
ZIP files.  Figure~\ref{fig:motivation} summarizes the 16 ZIP-related
vulnerabilities.
